Assessing rigor and impact of research software for hiring and promotion in psychology: A comment on Gärtner et al.~(2022)

### 2023-10-04 manuscript.Rmd
add conflict of interest statement

Add a statement about conflict of interest. If you have no conflict of interest to declare, please state that. Add a statement about how the research was funded. If there was no specific funding please state that.

>>>>

We have no conflict of interest to declare.
There was no specific funding for this research.
